---
title: "Final_Server_Sonia"
output:
  word_document: default
  html_notebook: default
---
BIS 581
#load libraries
```{r libs, echo=FALSE, message=FALSE, warning=FALSE}
library(tidytext)
library(ggplot2)
library(dplyr)
library(tidyr)
library(ggraph)
library(igraph)
```


```{r}
VDI <- read.csv("vdi_serverlogs.csv", header=TRUE, stringsAsFactors = FALSE)

apps <- read.csv("vdi_statsapps.csv", header=TRUE, stringsAsFactors = FALSE)
```


join the two together
```{r}
apps$VDI_ID <- as.integer(apps$VDI_ID)
usage <-  VDI %>% inner_join(apps)
#clean up

```
```{r}
##Viewing summary statistics of the data set
summary(usage)
```

```{r}
##Omitting NA'S (missing values) from data set
usage_1<-na.omit(usage)
```
**There are some missing values. I used na.omit to remove the missing values from the data set.**

```{r}
##Viewing summary statistics of the data set without missing values
summary(usage_1)
```
**Now there are no missing values.**

```{r}
##Converting the character to the Date class using the as.Date function
usage_1$logon_DTS=as.Date(usage_1$logon_DTS,"%m/%d/%y")
```
**I am not concerned with the time at this point but do want the date to be cast to a date type.**


```{r}
##Separating logon_DTS
date_login=separate(usage_1,logon_DTS,c("login.Year", "login.Month", "login.Day"), sep = "-")
```
**I separated the logon_DTS column by year, month and day to extract the 2015 data set.**


```{r}
##Extracting the 2015 data set
usage_2015<-date_login[date_login$login.Year=="2015",]
```
**Now the data set is for the year 2015.**



```{r}
##Trying to pick all words starting with 'CMU' from column comp_name
library(tidyverse)
##Creating a new data set where comp_name starts with 'CMU'
usage_2015%>% filter(str_detect(comp_name, "CMU"))  
usage_2015_CMU1<-usage_2015%>% filter(str_detect(comp_name, "CMU"))
```
**Now the data set is for the year 2015 and VDI machine only.**

```{r}
ggplot(data=usage_2015_CMU1, aes(avg_cpu))+geom_bar(stat = "bin")+ggtitle("Average CPU Time")
```

**The above graph is showing the average CPU usage by the users.**

**How many users were on the system total?**

```{r}
##Users on the system total
usage_2015_CMU1%>% count(userid)
```
```{r}
length(unique(usage_2015_CMU1$userid))
```
**There are total 3013 users on the system.**


**What is the average number of users per day?**

```{r}
##Combining 3 columns in 1 column
usage_2015_CMU11<-unite(usage_2015_CMU1,logon_DTS,c("login.Year","login.Month","login.Day"))
```

```{r}
usage_2015_CMU11%>%count(logon_DTS)
```
```{r}
length(unique(usage_2015_CMU11$logon_DTS))
```
**There are 223 days on system.**

```{r}
length(unique(usage_2015_CMU1$userid))/length(unique(usage_2015_CMU11$logon_DTS))
```


**There are 3013 total users on the system and 223 dates. The average number of users per day is  3013/223= 13.51**



**What is the highest number of users per day?**


```{r}
usage_2015_CMU11%>% count(logon_DTS)%>%  arrange(desc(n))
```
**The highest user was On April 28,2015 and the total number of users on that day was 5205.**


**A-D: top 5 users by number of times logged in, bottom 3 applications by length of time run**


```{r}
##Formatting dates and times
usage_2015_CMU11$Start_Hours <- format(as.POSIXct(usage_2015_CMU11$start,"%Y-%m-%d %H:%M:%S",tz = ""), format = "%H:%M")

usage_2015_CMU11$Stop_Hours <- format(as.POSIXct(usage_2015_CMU11$stop,"%Y-%m-%d %H:%M:%S",tz = ""), format = "%H:%M")
```


```{r}
##Returning the position of the specified values in the logical vector
which(usage_2015_CMU11$Stop_Hours=="00:00")
which(usage_2015_CMU11$Start_Hours=="00:00")
S1<-which(usage_2015_CMU11$Stop_Hours=="00:00")
S2<-which(usage_2015_CMU11$Start_Hours=="00:00")
usage_2015_CMU12<-usage_2015_CMU11[-c(S1,S2),]
```


```{r}
which(is.na(as.Date(usage_2015_CMU11$start)))
which(is.na(as.Date(usage_2015_CMU11$stop)))
```


```{r}
##Unclass stop_1
stop_1<-as.POSIXlt(usage_2015_CMU12$stop)
stop_11<-unclass(stop_1)
names(stop_11)
```

```{r}
##Unclass start_1
start_1<-as.POSIXlt(usage_2015_CMU12$start)
start_11<-unclass(start_1)
names(start_11)
```
**I did unclass for stop_1 and start_1.**

```{r}
stop_min<-stop_11$min
start_min<-start_11$min
stop_hour<-stop_11$hour
start_hour<-start_11$hour
```

```{r}
##Creating time difference to show the length of time run
diff_hour<-stop_hour-start_hour
diff_min<-stop_min-start_min
diff<-diff_min+(diff_hour*60)
usage_N=cbind(usage_2015_CMU12,diff)
```
**I created time difference in minutes to see the length of time run.**

```{r}
##Top 5 users by number of times logged in
usage_N%>% count(userid)%>% arrange(desc(n))
```
**The top 5 users by number of times logged in are 'userid5179', 'userid23588', 'userid25643', 'userid13479' and 'userid25647'.**


```{r}
##Bottom 3 applications by length of time run
usage_N%>%arrange(diff)
```
**The bottom 3 applications by length of time run are 'SnippingTool', 'POWERPNT' and 'iexplore'.**


